WASP-4 is Accelerating Towards the Earth

### 2020-02-03 paper/ms.tex
text: update observation descriptions

% FIXME : verify with Michael Gillon that this is true. (P. Evans
% done)
The majority of times are identical to those we collected in
\citetalias{bouma_wasp4b_2019}.  Twenty-two new times reported by
\citet{southworth_transit_2019} are included.  These transits were
observed from the 3.58m NTT and Danish 1.54m telescopes at La Silla,
and the SAAO 1.0m telescope.

@@

The complete set of radial velocity observations is given in Table~2.
Along with the 2010-2019 HIRES observations, there are also earlier
measurements from CORALIE and HARPS.  Following
\citetalias{bouma_wasp4b_2019}, we included the CORALIE measurements
from \citet{wilson_wasp-4b_2008} and \citet{triaud_spin-orbit_2010},
using the homogeneous radial velocities calculated by the latter
authors. We included the HARPS values reported by
\citet{pont_determining_2011} and \citet{husnoo_observational_2012}.
We omitted the HARPS data points taken over three nights by
\citet{triaud_spin-orbit_2010} for Rossiter-McLaughlin observations
because they have a systematic offset from the remaining datasets.

>>>>

% FIXME : verify with Michael Gillon that this is true. (P. Evans
% done)
The majority of times are identical to those we collected in
\citetalias{bouma_wasp4b_2019}.  Twenty-two new times reported by
\citet{southworth_transit_2019} are included.  These transits were
observed from the 3.58m NTT and Danish 1.54m telescopes at La Silla,
and the SAAO 1.0m telescope.
% Five of the twenty-two occurred at simultaneous epochs as transits
% previously reported by \citet{hoyer_tramos_2013}.

@@

The complete set of radial velocity observations is given in Table~2.
Along with the 2010-2019 HIRES observations, there are also
measurements from CORALIE and HARPS.  Following
\citetalias{bouma_wasp4b_2019}, we included the CORALIE measurements
from \citet{wilson_wasp-4b_2008} and \citet{triaud_spin-orbit_2010},
using the homogeneous radial velocities calculated by the latter
authors.

For HARPS, we included the values reported by
\citet{pont_determining_2011} and \citet{husnoo_observational_2012}.
While \citet{triaud_spin-orbit_2010} also acquired HARPS data over
three nights for Rossiter-McLaughlin observations, these data were
reduced with a non-standard pipeline, and so are systematically offset
from the remaining HARPS data.  In our final fit, we therefore omitted
the three \citet{triaud_spin-orbit_2010} nights.  We did nonetheless
experiment with using the recent \citet{trifonov_public_2020}
re-reductions, which allowed us to include two calibration RVs taken
as part of the \citet{triaud_spin-orbit_2010} program. The decision
regarding whether to include or omit these points did not
substantially affect any of our conclusions.
